---
title: Presentation title
author: John Doe
date: September 3rd, 1988
output:
  revealjs::revealjs_presentation:
    self_contained: false
    css: cnc.css
    highlight: pygments
    center: false
    # incremental: true
    # transition: slide
    reveal_plugins: ["search", "notes", "chalkboard"]
    reveal_options:
      width: 1920
      height: 1080
      # width: 960
      # height: 700
      chalkboard:
        theme: whiteboard
---

```{r include=FALSE}
library(tidyverse)
# NOTE: for a faster edit-preview cycle when authoring your presentation, you
# might want to temporarily disable these options altogether
knitr::opts_chunk$set(fig.width=8, fig.height=6, out.width=1200, out.height=900, dpi=300)
# knitr::opts_chunk$set(fig.width=8, fig.height=6, out.width=720, out.height=540, dpi=300)
```

<!------------------------ BEGIN PRESENTATION CONTENT ------------------------>

The default layout of this presentation is *widescreen*, **higher resolution**.
Toggle the commented `width` and `height` options above to achieve a more
traditional, "square" presentation layout. More information about the options
for reveal.js R Markdown presentations can be found at
<http://rmarkdown.rstudio.com/revealjs_presentation_format.html>.

Some revealjs plugins are included in the YAML header at the top just to give
an idea of how they should be used and what's available. Feel free to remove
any/all of them.

If you don't use any plugins, you can set `self_contained: true` in the YAML
header, which will allow you to just open the file with the presentation
locally, without having to run a server.

> - first-level headings (`=== / #`) are just section titles, they can't have
    content and can be navigated through horizontally
> - second-level headings (`--- / ##`) are titles for content slides nested
    within the individual sections; these can be navigated through vertically
    within each section
> - if the above doesn't make much sense, press `Esc` to see an overview of the
    presentation which hopefully will

Introduction
===============================================================================

YAML header config
-------------------------------------------------------------------------------

- `css` is the path to the CSS file which overrides the presentation styles to
  bring them in line with the CNC visual style
- `width` and `height`: these settings affect how much screen real estate the
  presentation content is allowed to take up.

Graphics setup
-------------------------------------------------------------------------------

- if you'll be using a single figure size throughout the presentation, it makes
  sense to change the chunk defaults once at the beginning with
  `opts_chunk$set()` instead of repeating the settings in per-chunk options
- general recommendations:
  1. keep `fig.{width,height}` relatively small (units of inches), so that font
     size remains large enough w.r.t. the plot (when increasing the size of the
     plot, font size isn't automatically scaled)
  2. set `out.{width,height}` to the actual display size you want to have in
     your presentation (in pixels); these values should take into account the
     overall size of the presentation canvas set by `width` and `height`, and
     obviously, they should keep the same aspect ratio as `fig.{width,height}`,
     otherwise your graphics will look stretched
  3. since you'll be stretching the original `fig.{width,height}` to
     `out.{width,height}` to display the figure, you should increase the `dpi`,
     otherwise the figure will look blurry

A *centered* figure
-------------------------------------------------------------------------------

<div class="centered">
```{r echo=FALSE}
qplot(1:10, 1:10)
```
</div>

Results
===============================================================================

Tables
-------------------------------------------------------------------------------

| This | is | a | header |
|------|----|---|--------|
| This | is | a | row    |

Code chunk echoing and two-column layouts
-------------------------------------------------------------------------------

<div class="container">

<div class="col">
```{r}
# this chunk will show both input and output
subset(mtcars, mpg > 30)
```
</div>

<div class="col">
```{r echo=FALSE}
# this chunk will only show output
subset(mtcars, mpg < 15)
```
</div>

</div>

Or three-column for all I care...
-------------------------------------------------------------------------------

<div class="container">

<div class="col">
```{r echo=FALSE}
subset(mtcars, mpg < 10)
```
</div>

<div class="col">
```{r echo=FALSE}
subset(mtcars, mpg >= 10 & mpg < 20)
```
</div>

<div class="col">
```{r echo=FALSE}
subset(mtcars, mpg > 20)
```
</div>

</div>

Centering
-------------------------------------------------------------------------------

Non-centered.

<div class="centered">
Centered.

Even multiple paragraphs.
</div>

Non-centered again.

Revealjs plugins
===============================================================================

Search
-------------------------------------------------------------------------------

The `search` plugin puts a search box in the upper left corner of the
screen which lets you quickly jump through textual matches to a query in your
presentation.

Notes
-------------------------------------------------------------------------------

The `notes` plugin adds a speaker notes view with timer and more goodies. It
opens in a separate browser window if you press the `S` key.

And this is how you create notes:

<aside class="notes">
### My fancy speaker notes

**WARNING**: Don't put level 1 and 2 Markdown headings in here because they will
be interpreted as slide delimiters!
</aside>

Chalkboard
-------------------------------------------------------------------------------

The `chalkboard` plugin lets you doodle either directly over your slide or on
an empty fresh virtual chalkboard. Use the buttons in the lower left corner or
the `C` and `B` keys to activate either of these options.

`Delete` clears the chalkboard. `Backspace` deletes all drawings on the current
slide. `D` downloads chalkboard drawings as JSON.

Note that this plugin doesn't seem to play well with the `search` plugin,
because it overlays the slide and thus makes the search box inaccessible.

<!------------------------- END PRESENTATION CONTENT ------------------------->

<script>
// this snippet ensures different styling for title slides
window.addEventListener("load", function() {
  var body = document.body;
  function tagBody(e) {
    if (!e.currentSlide.classList.contains("level2")) {
      body.classList.add("section-title");
    } else {
      body.classList.remove("section-title");
    }
  };
  var p = document.querySelectorAll("section.present");
  var e = { currentSlide: p[p.length - 1] };
  tagBody(e);
  Reveal.addEventListener("slidechanged", tagBody);
});
</script>