---
title: "Presentation title:"
subtitle: A tongue-in-cheek subtitle
author: [John Doe, Jane Doe]
date: September 3rd, 1988
output:
  revealjs::revealjs_presentation:
    self_contained: false
    template: pandoc_template.html
    css: cnc.css
    highlight: pygments
    center: false
    # incremental: true
    # transition: slide
    reveal_plugins: [search, notes, chalkboard]
    reveal_options:
      width: 1920
      height: 1080
      # width: 960
      # height: 700
      chalkboard:
        theme: whiteboard
---

```{r include=FALSE}
library(tidyverse)
# NOTE: for a faster edit-preview cycle when authoring your presentation, you
# might want to temporarily disable these options altogether
knitr::opts_chunk$set(fig.width=8, fig.height=6, out.width=1200, out.height=900, dpi=300)
# knitr::opts_chunk$set(fig.width=8, fig.height=6, out.width=720, out.height=540, dpi=300)
```

<!------------------------ BEGIN PRESENTATION CONTENT ------------------------>

**NB:** In order to automatically apply a special title slide style while
retaining PDF export functionality, this template ships with its own reveal.js
pandoc template in `pandoc_template.html`. If the presentation seems broken, it
may be because the [revealjs_presentation](https://github.com/rstudio/revealjs)
RMarkdown exporter has switched to a newer version of reveal.js in the
meantime. If that is the case, make sure you have this new version of the
template:

<https://github.com/rstudio/revealjs/blob/master/inst/rmarkdown/templates/revealjs_presentation/resources/default.html>

And tweak it in the same way as the original `pandoc_template.html` by adding
the snippet between the following pair of comments at the appropriate place:

```html
<!-- begin pandoc template customization -->
...
<!-- end pandoc template customization -->
```

Introduction
===============================================================================

General
-------------------------------------------------------------------------------

**Press `F` to go fullscreen.**

The default layout of this presentation is *widescreen*, **higher resolution**.
Toggle the commented `width` and `height` options above to achieve a more
traditional, "square" presentation layout. More information about the options
for reveal.js R Markdown presentations can be found at
<http://rmarkdown.rstudio.com/revealjs_presentation_format.html>.

Some revealjs plugins are included in the YAML header at the top just to give
an idea of how they should be used and what's available. Feel free to remove
any/all of them.

If you don't use any plugins, you can set `self_contained: true` in the YAML
header, which will allow you to just open the file with the presentation
locally, without having to run a server.

> - first-level headings (`=== / #`) are just section titles, they can't have
    content and can be navigated through horizontally
> - second-level headings (`--- / ##`) are titles for content slides nested
    within the individual sections; these can be navigated through vertically
    within each section
> - if the above doesn't make much sense, press `Esc` to see an overview of the
    presentation which hopefully will

YAML header config
-------------------------------------------------------------------------------

- `css` is the path to the CSS file which overrides the presentation styles to
  bring them in line with the CNC visual style
- `width` and `height`: these settings affect how much screen real estate the
  presentation content is allowed to take up.

Graphics setup
-------------------------------------------------------------------------------

- if you'll be using a single figure size throughout the presentation, it makes
  sense to change the chunk defaults once at the beginning with
  `opts_chunk$set()` instead of repeating the settings in per-chunk options
- general recommendations:
  1. keep `fig.{width,height}` relatively small (units of inches), so that font
     size remains large enough w.r.t. the plot (when increasing the size of the
     plot, font size isn't automatically scaled)
  2. set `out.{width,height}` to the actual display size you want to have in
     your presentation (in pixels); these values should take into account the
     overall size of the presentation canvas set by `width` and `height`, and
     obviously, they should keep the same aspect ratio as `fig.{width,height}`,
     otherwise your graphics will look stretched
  3. since you'll be stretching the original `fig.{width,height}` to
     `out.{width,height}` to display the figure, you should increase the `dpi`,
     otherwise the figure will look blurry

A *centered* figure
-------------------------------------------------------------------------------

<div class="centered">
```{r echo=FALSE}
qplot(1:10, 1:10)
```
</div>

Recommended deployment
-------------------------------------------------------------------------------

To generate the presentation, press the *Knit* button in RStudio or run
`rmarkdown::render("index.Rmd")` from an R prompt.

Some plugins (e.g. speaker notes) require that the presentation be served over
an HTTP connection. The recommended way to deploy it is therefore to drop **this
entire directory** into your `~/public_html` directory on a publicly accessible
server.

If you will be serving the presentation locally from your PC / laptop, the
easiest way to do so is probably from RStudio itself (just press *Knit* and it
will open). Alternatively, you can run a web server in this directory:

```sh
# depending on what you have installed
$ python2 -m SimpleHTTPServer
# or
$ python3 -m http.server
# or
$ php -S localhost:8000
```

You can then open the presentation by visiting <http://localhost:8000> in your
browser.

Single-file presentation
-------------------------------------------------------------------------------

**Don't do this.** Seriously. For viewing in the browser, use the [recommended
deployment](#recommended-deployment) method. For offline distribution, [export
to PDF](#exporting-to-pdf).

<small>

If you truly must, a single-file HTML version of the presentation, which can be
opened locally in a web browser without being served over HTTP (just by
double-clicking the file, on most systems), can be created by setting the
`self_contained` option in the YAML header to `true`. As mentioned on the
previous slide though, be aware that *some functionality* (e.g. speaker notes)
*might become unavailable*, and you may still need to *distribute external
resources* (such as images) along with the HTML file.

</small>

Results
===============================================================================

Tables
-------------------------------------------------------------------------------

| This | is | a | header |
|------|----|---|--------|
| This | is | a | row    |

Pretty-printing data frames with knitr::kable()
-------------------------------------------------------------------------------

```{r echo=FALSE, results="asis"}
knitr::kable(mtcars[1:5, ], caption="A knitr kable.")
```

Code chunk echoing and two-column layouts
-------------------------------------------------------------------------------

<div class="container">

<div class="col">
```{r}
# this chunk will show both input and output
subset(mtcars, mpg > 30)
```
</div>

<div class="col">
```{r echo=FALSE}
# this chunk will only show output
subset(mtcars, mpg < 15)
```
</div>

</div>

Or three-column for all I care...
-------------------------------------------------------------------------------

<div class="container">

<div class="col">
```{r echo=FALSE}
subset(mtcars, mpg < 10)
```
</div>

<div class="col">
```{r echo=FALSE}
subset(mtcars, mpg >= 10 & mpg < 20)
```
</div>

<div class="col">
```{r echo=FALSE}
subset(mtcars, mpg > 20)
```
</div>

</div>

Centering
-------------------------------------------------------------------------------

Non-centered.

<div class="centered">
Centered.

Even multiple paragraphs.
</div>

Non-centered again.

Revealjs plugins
===============================================================================

Search
-------------------------------------------------------------------------------

The `search` plugin puts a search box in the upper left corner of the
screen which lets you quickly jump through textual matches to a query in your
presentation.

Notes
-------------------------------------------------------------------------------

The `notes` plugin adds a speaker notes view with timer and more goodies. It
opens in a separate browser window if you press the `S` key.

And this is how you create notes:

<aside class="notes">
### My fancy speaker notes

**WARNING**: Don't put level 1 and 2 Markdown headings in here because they will
be interpreted as slide delimiters!
</aside>

Chalkboard
-------------------------------------------------------------------------------

The `chalkboard` plugin lets you doodle either directly over your slide or on
an empty fresh virtual chalkboard. Use the buttons in the lower left corner or
the `C` and `B` keys to activate either of these options.

`Delete` clears the chalkboard. `Backspace` deletes all drawings on the current
slide. `D` downloads chalkboard drawings as JSON.

Note that this plugin doesn't seem to play well with the `search` plugin,
because it overlays the slide and thus makes the search box inaccessible.

Conclusion
===============================================================================

Customizing individual slides {data-background="#000" data-background-iframe="https://youtube.com/embed/j3rwKl267gE?autoplay=1&controls=0&showinfo=0&autohide=1"}
-------------------------------------------------------------------------------

It's possible to customize backgrounds, transitions and other settings per
slide. See above for an example, and for more information, search for `{data-`
on [revealjs_presentation's website](https://github.com/rstudio/revealjs), or
for `data-` on [reveal.js's website](https://github.com/hakimel/reveal.js).

Characters with diacritics
-------------------------------------------------------------------------------

[Lato fonts](http://www.latofonts.com/) with full character sets are embedded,
so go nuts!

| Běžela Magda kaňonem,
| srážela banány rádiem.

Exporting to PDF
-------------------------------------------------------------------------------

1. Using Chrome/Chromium:¹ open the presentation with a `?print-pdf` or
   `?print-pdf&showNotes=true` query string, then print using the normal
   print dialog, adjusting settings for destination (*Save as PDF*),
   orientation, margins, background graphics etc. as necessary.
2. Use the [decktape](https://github.com/astefanutti/decktape) command line
   tool.

For more details on both methods, see
[reveal.js's GitHub](https://github.com/hakimel/reveal.js/#pdf-export).

<small>

¹ Or possibly any other browser, I think the primary reason for using Chrome or
Chromium is that it's relatively easy to alter the settings for a nice printout
without borders etc.

</small>

Thank you for your attention!
===============================================================================

<!------------------------- END PRESENTATION CONTENT ------------------------->
